% --------------------------------------------------------------------------
% Template for AASP Challenge extended abstracts; 
% to be used with: aasp.sty  - LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
%
% --------------------------------------------------------------------------

\documentclass{article}
\usepackage{aasp,amsmath,graphicx,url,times,epstopdf,cite}
%\usepackage{aasp,amssymb,amsmath,graphicx,times,url}

% Example definitions.
% --------------------
\def\defeqn{\stackrel{\triangle}{=}}
\newcommand{\symvec}[1]{{\mbox{\boldmath $#1$}}}
\newcommand{\symmat}[1]{{\mbox{\boldmath $#1$}}}

% Title.
% --------------------
\title{Event Detection and Classification}

% Single addresses (uncomment and modify for single-address case).
% --------------------
\name{Sameer Chauhan, Sharang Phadke, Christian Sherland\thanks{Thanks to the Cooper Union}}
\address{Author Affiliation(s)}

% For example:
% ------------
\address{Cooper Union for the Advancement of Science and Art\\
	Electrical Engineering\\
	41 Cooper Square\\
	New York, NY 10003}

% Two addresses
% --------------------
%\twoauthors
%  {John Doe\sthanks{Thanks to ABC agency for funding.}}
%    {ABC University\\
%     500 Rainy Street,\\
%     WC1 4AB London, UK \\
%     johndoe@abc.ac.uk}
%  {Jane Doe\sthanks{Thanks to XYZ agency for funding.}}
%    {XYZ University \\
%     3040 Westfield Avenue \\
%     New Paltz, NY, USA \\
%     janedoe@xyz.edu}

\begin{document}
\ninept
\maketitle

\begin{sloppy}

\begin{abstract}
\input{abstract}
\end{abstract}

\begin{keywords}
onset, offset, MFCCs, LRT
\end{keywords}

\section{Introduction}
\label{sec:intro}
\input{intro}

\section{Feature extraction}
\label{sec:feature}
\input{features}

\section{Training}
\label{sec:training}
\input{training}

\section{Segmentation}
\label{sec:segmentation}
\input{segmentation}

\section{Classification}
\label{sec:classification}
\input{classification}

\section{Results}
\label{sec:results}
\input{results}

\section{Conclusion}
\label{sec:conclusion}
\input{conclusion}

% Below is an example of how to insert images. 
% -------------------------------------------------------------------------

\section{REFERENCES}
\label{sec:ref}

List and number all bibliographical references at the end 
of the paper. The references should be numbered in order 
of appearance in the document. When referring to them in 
the text, type the corresponding reference number in 
square brackets as shown at the end of this sentence 
\cite{cJones2003}, \cite{aSmith2000}. For \LaTeX\ users, 
the use of the Bib\TeX\ style file IEEEtran.bst is 
recommended, which is included in the \LaTeX\ paper 
kit available from the workshop website \cite{aaspweb}.

\section{ACKNOWLEDGMENT}
\label{sec:ack}

Available Citations:
\cite{segmentFeature}  And 
\cite{silenceRemove} and
 \cite{prt2011} and 
\cite{discrimPRT} and
 \cite{dnn} and
 \cite{audioFeatures} and 
\cite{compModel}
\cite{rwEventD}
We would like to thank to Professor Sam Keene for his support and guidance. 
We would also like to thank New Folder Consulting for allowing us to use PRT.


% -------------------------------------------------------------------------
% Either list references using the bibliography style file IEEEtran.bst
%\bibliographystyle{IEEEtran}
%\bibliography{refsaasp}

% or list them by yourself
 \begin{thebibliography}{8}
\bibitem{silenceRemove}
	Theodoros Giannakopoulos, ``A method for silence removal and segmentation of speech signals, implemented in Matlab",\emph{ Department of Informatics and Telecommunications University of Athens, Greece|}, 2009. Software available at \url{https://www.mathworks.com/matlabcentral/fileexchange/28826-silence-removal-in-speech-signals}.

\bibitem{prt2011}
 Peter Torrione and Sam Keene and Kenneth Morton, ``{PRT}: The Pattern Recognition Toolbox for {MATLAB}", 2011. Software available at \url{http://newfolderconsulting.com/prt}.

\bibitem{segmentFeature}
 	Gordern Wichern, Jiachen Xue, Harvey Thornburg, Brandon Mechtley, and Andrewwas Spanias, ``Segmentation, Indexing, and Retrieval for Environmental and Natural Sounds" in \emph{"IEEE Trans. Signal Processing}, vol. 18, pp 688--707, March 2010.

\bibitem{audioFeatures}
 Theodoros Giannakopoulo, ``Some Basic Audio Features", Apr. 2008. Software available at \url{http://www.mathworks.com/matlabcentral/fileexchange/19236-some-basic-audio-features}

\bibitem{compModel}
Pampalk, Elias, ``Computational Models of Music Similarity and Their Application in Music Information Retrieval."\emph{Vienna University of Technology}, Mar. 2006

\bibitem{rwEventD}
Xiaodan Zhuang and Xi Zhou and Mark A and Hasegawa-Johnson and Thomas S. Huang, ``Real-world acoustic event detection", \emph{Pattern Recognition Letters} vol. 31, pp 1543--1551, Feb 2010

 \bibitem{dnn}
Geoffrey Hinton and Li Deng and Dong Yu and George Dahl and Abdel-rahman Mohamed and Navdeep Jaitly and Vincent Vanhoucke and Patrick Nguyen and Tara Sainath and Brian Kingsbury,  ``Deep Neural Networks for Acoustic Modeling in Speech Recognition,'' in \emph{IEEE Signal Processing Magazine}, pp. 82--97, Nov. 2012
 
 \bibitem{discrimPRT}
Xiaodong and Wu Chou. ``Discriminative Learning in Sequential Pattern Recognition,''  in \emph{IEEE Signal Processing Magazine}, pp. 14--36, Sept. 2008.
 
 \end{thebibliography}


\end{sloppy}
\end{document}
